---
title: "Assignment 6 : Web APIs"
author: "Khyati Naik"
date: "`r Sys.Date()`"
---


The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis
You’ll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.


### Read libraries

```{r load-packages, message=FALSE}
library(httr)
library(jsonlite)
library(tidyverse)
```

For this assignment, I chose the movie reviews New York Times APIs.

### Construct path to get movie reviews that are critics' picks

```{r}
api_movies <- "https://api.nytimes.com/svc/movies/v2/reviews/picks.json?api-key="
api_key <- "BJty2Wsivb3jXJ8YT5cHoraopLGGTpMl"
api_path <- paste(api_movies,api_key, sep = "")
```

### Read json data and convert it into R dataframe

```{r}
api_call <- fromJSON(api_path, flatten = TRUE) %>% data.frame()
```

### View the api data

```{r}
glimpse(api_call)
```


## Conclusion

In this assignment, I chose movie reviews New York Times API. Further, I generated the api key for the app. Finally, I read the json movie review data and converted into R dataframe.